The globular cluster system of the Auriga simulations

### 2020-04-06 AurigaGCS.tex
Refer to Sections 3.3, 3.4, 3.5 in first paragraph of Section 3. Thank referee for thoughtful and elaborate report.

\section{Observational data}
\label{sec:observations}
We describe the observations of the MW GCS in Section~\ref{sec:milkyway},
and of the M31 GCS in Section~\ref{sec:andromeda}

@@

\subsection{Age-estimates}
The top panel of Figure~\ref{fig:MW-M31-age-Rgc} shows a histogram of the age-estimates
of the $55$ MW GCs in V13 and $88$ GCs in M31 for which age-estimates are available
in CR16. The mean age of the MW GCs in this data set is $11.9 \pm 0.1$~Gyr and the 
dispersion is $0.8$~Gyr. Furthermore, only one of the 55 GC age-estimates is
below $10$~Gyr. The M31 GCS has a mean age of $11.0 \pm 0.2$~Gyr with a dispersion 
of $2.2$~Gyr, and $24$ GCs have age-estimates below $10$~Gyr with a minimum age 
of $4.8$~Gyr. Based on these data, we find that the age distributions of the MW 
and M31 GCSs are not statistically consistent. Moreover, the MW appears 
to host a GCS that is somewhat older than that of M31.
This is somewhat surprising given that M31 is generally considered to be earlier
type than the MW meaning that an older stellar population would be naively expected.
However, we do caution that both data sets are incomplete and the age 
measurements have large uncertainties (of $1-2$~Gyr). On the other hand, the 
magnitude of the uncertainty is insufficient to explain the low-age tail in M31.

@@

\section*{Acknowledgements}
TLRH acknowledges support from the International Max-Planck Research School (IMPRS)
on Astrophysics. TLRH thanks the Max Planck Computing and Data Facility for
maintaining the Freya compute cluster, where the simulations were post-processed.
FM is supported by the program "Rita Levi Montalcini" of the Italian MIUR. FAG 
acknowledges financial support from CONICYT through the project FONDECYT Regular 
Nr. 1181264, and funding from the Max Planck Society through a Partner Group grant.
This work has been supported by the European Research Council under ERC-StG grant
EXAGAL- 308037. Part of the simulations of this paper used the SuperMUC system 
at the Leibniz Computing Centre, Garching, under the project PR85JE of the Gauss 
Centre for Supercomputing. This work used the DiRAC Data Centric system at Durham
University, operated by the Institute for Computational Cosmology on behalf of
the STFC DiRAC HPC Facility `www.dirac.ac.uk'. This equipment was funded by BIS 
National E-infrastructure capital grant ST/K00042X/1, STFC capital grant 
ST/H008519/1 and STFC DiRAC Operations grant ST/K003267/1 and Durham University.
DiRAC is part of the UK National E-Infrastructure.

>>>>

\section{Observational data}
\label{sec:observations}
We describe the observations of the MW GCS in Section~\ref{sec:milkyway},
and of the M31 GCS in Section~\ref{sec:andromeda}. We discuss the age-estimates
in Section~\ref{sec:age}, the distribution of galactocentric radius in 
Section~\ref{sec:Rgc}, and the total mass in 2D bins of metallicity-galactocentric
radius in Section~\ref{sec:observations_FeHRgc}. We focus on metallicity and
galactocentric radius because these data are available in the observations and
in the Auriga simulations.

@@

\subsection{Age-estimates}
\label{sec:age}
The top panel of Figure~\ref{fig:MW-M31-age-Rgc} shows a histogram of the age-estimates
of the $55$ MW GCs in V13 and $88$ GCs in M31 for which age-estimates are available
in CR16. The mean age of the MW GCs in this data set is $11.9 \pm 0.1$~Gyr and the 
dispersion is $0.8$~Gyr. Furthermore, only one of the 55 GC age-estimates is
below $10$~Gyr. The M31 GCS has a mean age of $11.0 \pm 0.2$~Gyr with a dispersion 
of $2.2$~Gyr, and $24$ GCs have age-estimates below $10$~Gyr with a minimum age 
of $4.8$~Gyr. Based on these data, we find that the age distributions of the MW 
and M31 GCSs are not statistically consistent. Moreover, the MW appears 
to host a GCS that is somewhat older than that of M31.
This is somewhat surprising given that M31 is generally considered to be earlier
type than the MW meaning that an older stellar population would be naively expected.
However, we do caution that both data sets are incomplete and the age 
measurements have large uncertainties (of $1-2$~Gyr). On the other hand, the 
magnitude of the uncertainty is insufficient to explain the low-age tail in M31.

@@

\section*{Acknowledgements}
We thank the anonymous referee for a thoughtful and elaborate report that we feel
greatly improved the manuscript.
TLRH acknowledges support from the International Max-Planck Research School (IMPRS)
on Astrophysics. TLRH thanks the Max Planck Computing and Data Facility for
maintaining the Freya compute cluster, where the simulations were post-processed.
FM is supported by the program "Rita Levi Montalcini" of the Italian MIUR. FAG 
acknowledges financial support from CONICYT through the project FONDECYT Regular 
Nr. 1181264, and funding from the Max Planck Society through a Partner Group grant.
This work has been supported by the European Research Council under ERC-StG grant
EXAGAL- 308037. Part of the simulations of this paper used the SuperMUC system 
at the Leibniz Computing Centre, Garching, under the project PR85JE of the Gauss 
Centre for Supercomputing. This work used the DiRAC Data Centric system at Durham
University, operated by the Institute for Computational Cosmology on behalf of
the STFC DiRAC HPC Facility `www.dirac.ac.uk'. This equipment was funded by BIS 
National E-infrastructure capital grant ST/K00042X/1, STFC capital grant 
ST/H008519/1 and STFC DiRAC Operations grant ST/K003267/1 and Durham University.
DiRAC is part of the UK National E-Infrastructure.
